Analysis for Project

### 2021-11-17 analysis/analysis.Rmd
Don't use weights in estimation

```{r desc-stats}
tbl_summary <- acs %>%
  group_by(race) %>%
  summarize(n=n(), 
            held_back=round(mean(below_exp_grade), 3)*100,
            mean_age=round(mean(age), 1),
            f_born=round(mean(foreign_born), 3)*100,
            par_fb=round(mean(foreign_born_father | 
                                       foreign_born_mother), 3)*100,
            fam_inc=round(mean(family_income), 0),
            own_home=round(mean(own_home), 3)*100,
            par_hs=round(mean(degree_father!="LHS" | 
                                degree_mother!="LHS"), 3)*100,
            par_ba=round(mean(degree_father=="BA" | 
                                degree_father=="G" | 
                                degree_mother=="BA" | 
                                degree_mother=="G"), 3)*100,
            par_mar=round(mean(parents_married), 3)*100) %>%
  arrange(desc(n))

@@

design_matrix <- cbind(states, years, grades, metro, degree)

@@

#TODO: It won't let me add strata - gives some error. This sucks because 
#strata may help to reduce SEs
design_matrix <- svydesign(ids=~cluster, weights=~perwt, data=design_matrix)

```

@@

```{r build-models, results='asis'}
model0 <- svyglm(below_exp_grade~race, design=design_matrix, family=binomial)
model1 <- update(model0, 
                 .~.+y2011+y2012+y2013+y2014+y2015+y2016+y2017+y2018+y2019+
                   current_grade1st+current_grade2nd+current_grade3rd+
                   current_grade4th+current_grade5th+current_grade6th+
                   current_grade7th+current_grade8th+current_grade9th+
                   current_grade10th+current_grade11th+current_grade10th+
                   current_grade11th+current_grade12th+
                   met_non_metro+met_central_city+met_non_central_city+
                   met_city_indeter+
                   s1+s2+s3+s4+s5+s6+s7+s8+s9+s10+s11+s12+s13+s14+s15+s16+s17+
                   s18+s19+s20+s21+s22+s23+s24+s25+s26+s27+s28+s29+s30+s31+s32+
                   s33+s34+s35+s36+s37+s38+s39+s40+s41+s42+s43+s44+s45+s46+s47+
                   s48+s49+s50)
model2 <- update(model1, .~.+foreign_born+foreign_born_mother+
                   foreign_born_father)
model3 <- update(model2, .~.+degree_motherHS+degree_motherAA+degree_motherBA+
                   degree_motherG+degree_fatherHS+degree_fatherAA+
                   degree_fatherBA+degree_fatherG)
model4 <- update(model3, .~.+income_trans+own_home+parents_married)

@@

```{r create-predictor-data}
#dateset for predict
df_pred <- data.frame(race=levels(acs$race),
                      y2011=0, y2012=0, y2013=0, y2014=0, y2015=0, y2016=0,
                      y2017=0, y2018=0, y2019=0,
                      current_grade1st=0, current_grade2nd=0, current_grade3rd=0,
                      current_grade4th=0, current_grade5th=0, current_grade6th=0,
                      current_grade7th=0, current_grade8th=0, current_grade9th=0,
                      current_grade10th=0, current_grade11th=0, current_grade12th=0,
                      met_non_metro=0, met_central_city=0, met_non_central_city=0,
                      met_city_indeter=0,
                      s1=0, s2=0, s3=0, s4=0, s5=0, s6=0, s7=0, s8=0, s9=0, s10=0,
                      s11=0, s12=0, s13=0, s14=0, s15=0, s16=0, s17=0, s18=0, s19=0,
                      s20=0, s21=0, s22=0, s23=0, s24=0, s25=0, s26=0, s27=0, s28=0,
                      s29=0, s30=0, s31=0, s32=0, s33=0, s34=0, s35=0, s36=0, s37=0,
                      s38=0, s39=0, s40=0, s41=0, s42=0, s43=0, s44=0, s45=0, s46=0,
                      s47=0, s48=0, s49=0, s50=0,
                      degree_motherHS=0, degree_motherAA=0, degree_motherBA=0,
                      degree_motherG=0, degree_fatherHS=0, degree_fatherAA=0, 
                      degree_fatherBA=0, degree_fatherG=0,
                      foreign_born=0, foreign_born_father=0, foreign_born_mother=0,
                      income_trans=0, own_home=0, parents_married=0)
```

>>>>

```{r desc-stats}
tbl_summary <- acs %>%
  group_by(race) %>%
  summarize(n=n(), 
            held_back=round(mean(below_exp_grade), 3)*100,
            mean_age=round(mean(age), 1),
            f_born=round(mean(foreign_born), 3)*100,
            spk_eng_well=round(mean(spk_eng=="Yes"), 3)*100,
            spk_eng_par=round(mean(spk_eng_father=="Yes" & 
                                     spk_eng_mother=="Yes"), 3)*100,
            par_fb=round(mean(foreign_born_father | 
                                       foreign_born_mother), 3)*100,
            fam_inc=round(mean(family_income), 0),
            own_home=round(mean(own_home), 3)*100,
            par_hs=round(mean(degree_father!="LHS" | 
                                degree_mother!="LHS"), 3)*100,
            par_ba=round(mean(degree_father=="BA" | 
                                degree_father=="G" | 
                                degree_mother=="BA" | 
                                degree_mother=="G"), 3)*100,
            par_mar=round(mean(parents_married), 3)*100) %>%
  arrange(desc(n))

@@

spk_eng <- model.matrix(~spk_eng+spk_eng_father+spk_eng_mother, acs)[,-1]
#mean center
spk_eng <- t(t(spk_eng)-apply(spk_eng, 2, mean))
spk_eng <- as.data.frame(spk_eng)

design_matrix <- cbind(states, years, grades, metro, degree, spk_eng)

@@

design_matrix <- svydesign(ids=~cluster, data=design_matrix)
```

@@

```{r build-models, results='asis'}
model0 <- svyglm(below_exp_grade~race, design=design_matrix, family=binomial)
model1 <- update(model0, 
                 .~.+y2011+y2012+y2013+y2014+y2015+y2016+y2017+y2018+y2019+
                   current_grade1st+current_grade2nd+current_grade3rd+
                   current_grade4th+current_grade5th+current_grade6th+
                   current_grade7th+current_grade8th+current_grade9th+
                   current_grade10th+current_grade11th+current_grade10th+
                   current_grade11th+current_grade12th+
                   met_non_metro+met_central_city+met_non_central_city+
                   met_city_indeter+
                   s1+s2+s3+s4+s5+s6+s7+s8+s9+s10+s11+s12+s13+s14+s15+s16+s17+
                   s18+s19+s20+s21+s22+s23+s24+s25+s26+s27+s28+s29+s30+s31+s32+
                   s33+s34+s35+s36+s37+s38+s39+s40+s41+s42+s43+s44+s45+s46+s47+
                   s48+s49+s50)
model2 <- update(model1, .~.+foreign_born+foreign_born_mother+
                   foreign_born_father+spk_engSomewhat+spk_engYes+
                   spk_eng_motherSomewhat+spk_eng_motherYes+
                   spk_eng_fatherSomewhat+spk_eng_fatherYes)
model3 <- update(model2, .~.+degree_motherHS+degree_motherAA+degree_motherBA+
                   degree_motherG+degree_fatherHS+degree_fatherAA+
                   degree_fatherBA+degree_fatherG)
model4 <- update(model3, .~.+income_trans+own_home+parents_married)

@@

```{r create-predictor-data}
#dateset for predict
df_pred <- data.frame(race=levels(acs$race),
                      y2011=0, y2012=0, y2013=0, y2014=0, y2015=0, y2016=0,
                      y2017=0, y2018=0, y2019=0,
                      current_grade1st=0, current_grade2nd=0, current_grade3rd=0,
                      current_grade4th=0, current_grade5th=0, current_grade6th=0,
                      current_grade7th=0, current_grade8th=0, current_grade9th=0,
                      current_grade10th=0, current_grade11th=0, current_grade12th=0,
                      met_non_metro=0, met_central_city=0, met_non_central_city=0,
                      met_city_indeter=0,
                      s1=0, s2=0, s3=0, s4=0, s5=0, s6=0, s7=0, s8=0, s9=0, s10=0,
                      s11=0, s12=0, s13=0, s14=0, s15=0, s16=0, s17=0, s18=0, s19=0,
                      s20=0, s21=0, s22=0, s23=0, s24=0, s25=0, s26=0, s27=0, s28=0,
                      s29=0, s30=0, s31=0, s32=0, s33=0, s34=0, s35=0, s36=0, s37=0,
                      s38=0, s39=0, s40=0, s41=0, s42=0, s43=0, s44=0, s45=0, s46=0,
                      s47=0, s48=0, s49=0, s50=0,
                      degree_motherHS=0, degree_motherAA=0, degree_motherBA=0,
                      degree_motherG=0, degree_fatherHS=0, degree_fatherAA=0, 
                      degree_fatherBA=0, degree_fatherG=0,
                      foreign_born=0, foreign_born_father=0, foreign_born_mother=0,
                      spk_engSomewhat=0, spk_engYes=0, spk_eng_fatherSomewhat=0, 
                      spk_eng_fatherYes=0, spk_eng_motherSomewhat=0, spk_engYes=0,
                      income_trans=0, own_home=0, parents_married=0)
```
